\section{Experience}

	\runsubsection{Twilio, Incorporated}
    \descript{Staff Software Engineer}
    \location{Apr 2024 – present | San Luis Obispo, CA}
    \begin{tightemize}
      \item Designing data schemas in OLAP databases for highly performant querying and dataviz applications.
      \item On-call responsibility to manage observability and uptime for team owned services, debugging and resolving SEVs.
      \item Maintaining multiple self hosted, highly replicated and sharded Clickhouse DB platform on Kubernetes for other engineering teams to use.
      \item Maintaining a Trace DB like system for other engineering teams to use for contact tracing in their business logic with BCR and GDPR compliance.
      \item Providing Clickhouse APIs and RPC servers for ingestion, querying, schema migrations control, backups, monitoring and alerting.
      \item Worked on transforming the single cluster, multi-domain architecture to multi-cluster single domain architecture for clickhouse allowing us to cost-optimize. This allowed us to achieve a cloud COGS savings of 24\% and increase query speed by 29\% on average.
      \item Skills used: Ruby, Go, Kubernetes, Helm, Zookeeper, Kafka, gRPC, Distributed systems.
    \end{tightemize}
    \sectionsep

	\runsubsection{Twilio, Incorporated}
    \descript{Senior Software Engineer}
    \location{Sep 2022 – Apr 2024 | Santa Barbara, CA}
    \begin{tightemize}
      \item Working on CDP Analytics platform, creating and maintaining high throughput data ingestion pipelines.
      \item On-call responsibility to manage observability and uptime for team owned services.
      \item As an SME for analytics platform, I was able to consult on a sev that is affecting a churn risk customer, quickly debugged the upstream data source issue and implement a quick fix to the systems while the upstream gets fixed thereby maintaining customer satisfaction.
      \item Re-designed and re-implemented a v2 ingestion pipeline that decreased memory requirements for querying by 100\%, added deduplication and made the query results deterministic.
      \item Created a new deployment pattern for multi-deployments within the same codebase while being backwards compatible with the existing GitOps deployment flow.
      \item Skills used: Ruby, Go, React, Kubernetes, GraphQL, gRPC.
    \end{tightemize} 
    \sectionsep

	\runsubsection{Teladoc Health}
    \descript{Software Engineer III, Engineering Tech Lead}
    \location{Nov 2021 – Sep 2022 | Santa Barbara, CA}
    \begin{tightemize}
      \item Leading two teams simultaneously - web platform and maintenance of value added services.
      \item Worked on breaking down the react SPA's global state management to use smaller domain driven stores reducing unwanted re-renders and improving performance by 200\%.
      \item Skills used: Rails, React, Node and other database and deployment technologies.
    \end{tightemize} 
    \sectionsep

	\runsubsection{Appfolio Incorporated}
    \descript{Software Engineer I and II}
    \location{Jul 2017 – Nov 2021 | Santa Barbara, CA}
    \begin{tightemize}
      \item Worked with AppFolio tenant screening product infrastructure and product team.
      \item Lead multiple third party integrations and compliance related goals under deadlines while on-call.
      \item Co-created the data vendor fallback pattern that auto switches to the next available vendor when the primary vendor is down, reducing our outage incidents to effectively zero.
      \item Created and maintained many open source gems for use in company and ruby community.
      \item Created circle CI plugin to warn when adding code not compatible with the next rails version.
      \item Co-Created full featured internal tool to help public record analysts to manage customer interactions regarding screening reports, this reduced the customer turn around time from 3 days to 1 hour.
      \item Mentored many summer interns and helped with onboarding of new hires.
      \item Skills used: Rails, React, Node and other database technologies.
    \end{tightemize} 
    \sectionsep

	% \runsubsection{Procore Technologies}
  %   \descript{Software Engineering Intern}
  %   \location{Mar 2017 – Jun 2017 | Carpinteria, CA}
  %   \begin{tightemize}
  %     \item Participated in Agile sprints, working on both front-end and back-end tickets.
  %     \item Implemented new features, improved existing modules and shipped production quality code.
  %     \item Skills used: Node, React, Redux, Rails, PostgreSQL.
  %   \end{tightemize}
  %   \sectionsep

	% \runsubsection{UC Irvine}
  %   \descript{| Teaching Assistant, EECS114 - Algorithms and Data Structures}
  %   \location{Sep 2016 – Dec 2016 | Irvine, CA}
  %   \begin{tightemize}
  %     \item Instructed two lab sessions, prepared Assignments and held office hours
  %     \item Skills used: Algorithms, Data Structures, Java.
  %   \end{tightemize}
  %   \sectionsep
