% !TEX program = xelatex

\documentclass[]{base}
\usepackage{graphicx}
\graphicspath{ {checksum/} }

\begin{document}
\namesection {}{Joel Bandi}{\urlstyle{same}\url{http://joelbandi.github.io} | \href{mailto:joelvivekbandi@gmail.me}{joelvivekbandi@gmail.com}}

\begin{minipage}[t]{0.33\textwidth}
	\section{Education} 
	
	\subsection{UC Irvine}
	\descript{MS in Computer Engineering}
	\location{Dec 2016 | Irvine, CA \\ Cum. GPA: 3.48/4.00}
	\sectionsep
	
	\subsection{IFHE University}
	\descript{B.Tech in Electronics and Communication}
	\location{July 2015 | Hyderabad, India}
	\location{ Cum. GPA: 9.71/10.0}
	\location{Magna Cum Laude Honors}
	\sectionsep
	
	\section{Coursework}
	\subsection{Graduate}
	Projects in Web Applications (CS122B) \\
	Next Generation Search Systems (CS225) \\
	Design and Analysis of Algorithms (EECS215) \\
	Distributed and Middleware systems (CS237) \\
	Software for Embedded Systems (CS245) \\
	Software Analysis and Testing (IN4MATX215) \\
	High Performance Architecture (CS243) \\
	Analysis of Programming Languages (EECS228) \\
	\subsection{Online}
	Web Tooling \& Automation -Udacity\\
	Offline Web application -Udacity
	
	\sectionsep
	
	\section{Skills}
	\subsection{Programming}
	\location{Primary skill set:}
	Java | Js | Ruby | Elixir \\
	\location{Proficient in:}
	CSS/Sass | HTML | SQL | NoSQL | Bash \\
	\location{Frameworks and tools:}
	NPM | Git | React | Redux | ES6 | Android | AWS | Docker | Redis | Express | Rails
	\section{Links}
	\subsection{LinkedIn}
	\urlstyle{same}\url{https://linkedin.com/in/joelbandi}\\
	\subsection{Github}
	\urlstyle{same}\url{https://github.com/joelbandi}\\
	\subsection{Blog}
	\urlstyle{same}\url{https://joelbandi.github.io/trickshots}\\
	
	
\end{minipage}
\begin{minipage}[t]{0.66\textwidth} 
	
	
	\section{Experience}
	
	\runsubsection{Appfolio Incorporated}
	\descript{Software Engineer}
	\location{Jul 2017 – present | Santa Barbara, CA}
	\vspace{\topsep}
	\begin{tightemize}
		\item working with the core product and financial infrastructure team
		\item Skills used: Rails, React, Node and other database technologies.
	\end{tightemize}
	\sectionsep
	
	\runsubsection{Procore Technologies}
	\descript{Software Engineering Intern}
	\location{Mar 2017 – Jun 2017 | Carpinteria, CA}
	\vspace{\topsep}
	\begin{tightemize}
		\item Worked on core product with the Insights team (web-rails).
		\item Participate in Agile sprints, working on both front-end and back-end tickets.
		\item Implemented new features, improved existing modules and shipped production quality code.
		\item Skills used: Node, React, Redux, Rails, PostgreSQL.
	\end{tightemize}
	\sectionsep
	
	\runsubsection{UC Irvine}
	\descript{| Teaching Assistant, EECS114 - Algorithms and Data Structures}
	\location{Sep 2016 – Current | Irvine, CA}
	% \vspace{\topsep} % Hacky fix for awkward extra vertical space
	\begin{tightemize}
		\item Instructing two lab sessions.
		\item Prepared Assignments and held office hours.
		\item Skills used: Algorithms, Data Structures, Java.
	\end{tightemize}
	\sectionsep
	
	\runsubsection{UC Irvine}
	\descript{| Grader, EECS40 - Object Oriented Programming using Java and Android }
	\location{Mar 2016 – Jun 2016 | Irvine, CA}
	\begin{tightemize}
		\item Assisted students in using github, android tidbits and project management.
		\item Built, tested and graded android games designed by students.
		\item Skills used: Bash, Java.
	\end{tightemize}
	\sectionsep
	
	
	\section{Course Projects}
	\runsubsection{‘The Movie Mafia’ Online Movie Store} \\
	\begin{tightemize}
		\item Built an end to end MVC inspired web application completely from the scratch
		\item Designed to communicate with a MySQL database running in AWS using an Apache Tomcat container.
		\item Built and augmented web interface with functionality like pop-ups, typeaheads with auto-complete, fuzzy searching.
		\item Also built a feature rich android client for the web application.
	\end{tightemize}
	\sectionsep
	
	\runsubsection{Meet}
	\begin{tightemize}
		\item A P2P server based hyperlocal app that connects like-minded people within each other’s vicinity using Facebook profile matching and a custom recommendation engine.
		\item Written a Node.js and Express backend RESTful API and deployed on Heroku platform
		\item Built a P2PKit enabled Android front-end client capable of detecting users nearby while querying the backend for ranked profiles of detected users.
	\end{tightemize}
	
	\sectionsep\
	
\end{minipage} 

\end{document}  \documentclass[]{article}
